Everthing you wanted to know about PanDA but were truly truly afraid to ask

### 2016-11-08 bckground.tex

\paragraph*{Workload Vs Workflow} The term ``workflow'' is used in many
disciplines with different meaning. In the field of scientific computing,
``workflow'' assumes different meanings depending on the characteristics of the
computation, of the software tools used to support this computation, and of the
resources on which it is performed. Further, a workflow may indicate a whole
application, a description of the computational process of that application or,
more commonly, a series of tasks related by data dependences.

@@

@@

Workload managers are those components of workflow systems or, more in general, of distributed applications that enable resource selection.

\subsection{ATLAS Workflow}

>>>>

\subsection{Workflows and Workloads}

The term ``workflow'' is used in many disciplines with different meaning. In the
field of scientific computing, ``workflow'' assumes different meanings depending
on the characteristics of the computation, of the software tools used to support
this computation, and of the resources on which it is performed. Further, a
workflow may indicate a whole application, a description of the computational
process of that application or, more commonly, a series of tasks related by data
dependences.

@@

\subsection{The ATLAS Monte Carlo Workflow}

@@

Workload managers are those components of workflow systems or, more in general,
of distributed applications that enable resource selection, acquisition, and
use. The set of capabilities required by a workload manager mostly depends on
the heterogeneity and dynamicity of both the workflow and the resources.
Heterogeneity is a measure of the diversity of the workflow requirements and
resource capabilities that need to be matched to enable the execution of the
workflow's tasks; dynamicity is a measure of how much these requirements and
capabilities varies during execution.

The PanDA workload management system was initially designed to manage the execution of static, relatively homogeneous tasks on dynamic but homogeneous resources. Progressively, PanDA has evolved to enable the management of more heterogeneous tasks and resources. In this paper we describe how the design and architecture of PanDA has enabled executions of multi-threaded tasks on Titan, currently the largest high performance computing (HPC) resource available in the USA for scientific research.
